Avoiding tipping points in ecosystem based fisheries management: a non-parametric Bayesian approach

### 2014-05-12 manuscripts/manuscript.Rmd
rename sims figure

```{r Figure3, dependson=c("sim"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model.",  include=TRUE, echo=FALSE}

@@

For simplicity we assume profit function $\Pi_t(X_t, h_t) is linear in the realized harvest, only
enforcing the restriction that harvest can not exceed available stock, that is $\Pi(h,x) = min(h,x)$. $Z_t$ is as previously defined.

>>>>

```{r simsFigure, dependson=c("sim"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model.",  include=TRUE, echo=FALSE}

@@

For simplicity we assume profit function $\Pi_t(X_t, h_t)$ is linear in the realized harvest, only
enforcing the restriction that harvest can not exceed available stock, that is $\Pi(h,x) = \min(h,x)$. $Z_t$ is as previously defined.
